Type Refinements for the Working Class

### 2015-12-23 paper.tex
Define the type of atoms

\subsection{Example: Dependent Function Types}
\newcommand\SortArr[2]{#1\rightharpoonup #2}
\newcommand\OpLambda[2]{\mathtt{lam}_{#1}^{#2}}
\newcommand\OpAp[2]{\mathtt{ap}_{#1}^{#2}}

>>>>

\subsection{Examples of refinements and their typehood}

We will demonstrate how to define certain refinements, and prove that they are
types.

\subsubsection{The type of atoms}
\newcommand\SortAtom{\mathtt{atom}}
\newcommand\OpToken[1]{\mathtt{tok}[#1]}
\newcommand\OpMatch[1]{\mathtt{match}_{#1}}

Fix an extensional lcs whose signature contains the following:
\[
  \infer{
    \IsSort{\SortAtom}
  }{
  }
\]
\[
  \infer{
    \IsCanOperator{\Upsilon,a:\SortAtom}{
      \OpToken{a}
    }{
      \MkArity{}{\SortAtom}
    }
  }{
  }
  \qquad
  \infer{
    \IsOperator{\Upsilon}{
      \OpMatch{\tau}
    }{
      \MkArity{
        \MkValence{}{}{\SortAtom};
        \MkValence{}{}{\tau};
        \MkValence{}{}{\tau}
      }{\tau}
    }
  }{
    \IsSort{\tau}
  }
\]

Then, we can define a refinement $\GloballyRefines{\mathbb{A}_0}{\SortAtom}$ as
follows:
\[
  \infer{
    \RMemEq{\Upsilon}{
      \App{\OpToken{a}}{}
    }{
      \App{\OpToken{a}}{}
    }{\mathbb{A}_0}
  }{
    \IMode{\Upsilon}\ni\IMode{a}:\IMode{\SortAtom}
  }
\]

However, it is not the case that $\mathbb{A}_0$ is a type, because it doesn't
respect computational equivalence. This is easily resolved by defining the type
of atoms as the computational extension of $\mathbb{A}_0$,
\[
  \Define{
    \mathbb{A}
  }{
    \VToCType(\mathbb{A}_0)
  }
\]

\begin{thm}
  For any $\Upsilon$, we have $\IsType{\Upsilon}{\mathbb{A}}{\SortAtom}$.
\end{thm}
\begin{proof}
  Trivial, because the computational extension of any value PER is a type.
\end{proof}

\subsubsection{Dependent function types}
\newcommand\SortArr[2]{#1\rightharpoonup #2}
\newcommand\OpLambda[2]{\mathtt{lam}_{#1}^{#2}}
\newcommand\OpAp[2]{\mathtt{ap}_{#1}^{#2}}
